A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-02-17 paper/paper.tex
We've got room to make this a bit nicer

Let $\graphG$ and $\graphH$ be the two input graphs to our maximum common subgraph problem.
The orders (vertex counts) of these graphs are denoted $g$ and $h$.

>>>>

Throughout, $\graphG$ and $\graphH$ will be the two input graphs to our maximum
common subgraph problem.  The orders (number of vertices) of these graphs are
denoted $g$ and $h$ respectively.
